\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Analysis of the Ants Colony Algorithm\\
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Josue Guerrero}
\IEEEauthorblockA{\textit{Computer Engineering School} \\
\textit{Instituto Tecnologico de Costa Rica}\\
Cartago, Costa Rica \\
josueggss73@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Jorge Gutierrez}
\IEEEauthorblockA{\textit{Computer Engineering School} \\
\textit{Instituto Tecnologico de Costa Rica}\\
Cartago, Costa Rica \\
jorgeedugutima15@ieee.org}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits. 

\section{Related Work}
\section{Proposed method}
\subsection{Analysis of the Algorithm}
\section{Experiments}
\section{Results}
\section{Discussion}
\section{Conclusions}
\section{Future work}

%%Example of Bibliography 
\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\end{thebibliography}

\end{document}
